General constraints on magic distillation protocols from statistical mechanics

### 2021-05-03 magic_paper.tex
minor changes

Therefore, the action of $\E$ sending $\tau^{\otimes n}$ to $\sigma^{\otimes m}$ is viewed in terms of $\Delta H \coloneqq H'-H$, which is the Hamiltonian change that would be needed to adiabatically restore equilibrium at temperature $T$.
Given this account of the physical ingredients of a distillation protocol, we now state the following result for the case of qutrits.
\begin{theorem}\label{thm:free-energy}
	Consider a magic distillation protocol that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$. Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem.
Assume for $n,m \rightarrow \infty$ that the protocol's channel $\E$ generates negligible correlations on the equilibrium state and so there is a state $\tau'$ such that
\begin{equation}
	\tau^{\otimes n} \longrightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}
\end{equation} 
for $n,m \gg 1$. We write the output state as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.

>>>>

Therefore, the action of $\E$ sending $\tau^{\otimes n}$ to $\sigma^{\otimes m}$ is viewed in terms of $\Delta H \coloneqq H'-H$, which is the Hamiltonian change that would be needed to adiabatically restore equilibrium at temperature $T$.
Given this account of the physical ingredients of a distillation protocol, we now state the following result for the case of qutrits.
\begin{theorem}\label{thm:free-energy}
	Consider a magic distillation protocol that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$. Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem.

Assume for $n,m \rightarrow \infty$ that the protocol's channel $\E$ generates negligible correlations on the equilibrium state, so there is a state $\tau'$ such that
\begin{equation}
	\tau^{\otimes n} \longrightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}
\end{equation} 
for $n,m \gg 1$. 
We write the output state as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
